### 2016-11-15 report/survey.tex
Started framework for survey paper. Need to automatically generate the tables.

>>>>

\section{Arya}
Below are the preliminary results by running two benchmarks on the research computer Arya.

Machine Specifications

% TODO: Get this to be filled out automatically wherever possible.

\begin{tabular}{lr}
CPU & 72 Core Intel Xeon E5 2699 v3\\ \hline
RAM & 256 GB DDR4 ? MHZ
\end{tabular}

Report Card

\begin{tabular}{lr}
Transport & \\ \hline
Network Topology & \\ \hline
Local Scheduling & \\ \hline
Runtime Feedback & \\ \hline
Approach & \\ \hline
Algorithmic Considerations & \\ \hline
\end{tabular}

Performance in millions of traversed edges per second (MTEPS)

\begin{tabular}{l|r|r}
 & PowerGraph & OpenG \\ \hline
BFS & $87.4$ & $341$ \\ \hline
SSSP & $1.09$ & $3.08$ \\ \hline
\end{tabular}

The
